\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-09-27 gwnnDraft02.tex
edits

Dylan.linthorne@carleton.ca \\

@@

Cosmological observations, particularly limits on extra relativistic degrees of freedom at the time of Big Bang Nucleosynthesis and the time of the formation of the cosmic microwave background (CMB)~\cite{Aghanim:2018eyx}, require that most of the energy in the universe is in the Standard Model sector as we will quantify. Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector. This can be accomplished using inflationary axion-like particle (ALP) models~\cite{MARSH20161,PhysRevLett.121.201303} or the reheaton method~\cite{Arkani-Hamed:2016rle}. We will also explore alternative parameterizations of reheating that satisfy this condition.

@@

where $\Lambda$ is some high scale cutoff, $N$ is the number of sectors, and $r$ mass parameter in the SM in units of $\Lambda_H^2/N$. We view the parameterization of Eq.~(\ref{eqn:massParam}) as a random distribution in theory space up to the cutoff $\Lambda$, therefore this setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$~\cite{Arkani-Hamed:2016rle}\footnote{Constraints require $r$ to be somewhat smaller than 1.} and our sector is the one that that has the smallest absolute value of the Higgs mass parameter. We have taken for simplicity that there equal numbers sectors with positive and negative $m_H^2$, but this assumption does not affect our analysis. This $N$naturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder. The one exception to this is that ``our" sector must consist of the Standard Model.

@@

The ``exotic sectors'' with $i<0$ provide a radical departure from our own. $m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances. The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet. This leads to very light fermions: 

>>>>

DylanLinthorne@cmail.carleton.ca \\

@@

Cosmological observations, particularly limits on extra relativistic degrees of freedom at the time of Big Bang Nucleosynthesis and the time of the formation of the cosmic microwave background (CMB)~\cite{Aghanim:2018eyx}, require that most of the energy in the universe is in the Standard Model sector as we will quantify. Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector. This can be accomplished using inflationary axion-like particles (ALP)~\cite{MARSH20161,PhysRevLett.121.201303} or the reheaton method~\cite{Arkani-Hamed:2016rle}. We will also explore alternative parameterizations of reheating that satisfy this condition.

@@

where $\Lambda$ is some high scale cutoff, $N$ is the number of sectors, and $r$ mass parameter in the SM in units of $\Lambda_H^2/N$. We view the parameterization of Eq.~(\ref{eqn:massParam}) as a random distribution in theory space up to the cutoff $\Lambda$, therefore this setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$~\cite{Arkani-Hamed:2016rle}\footnote{Constraints require $r$ to be somewhat smaller than 1.} and our sector is the one that that has the smallest absolute value of the Higgs mass parameter. We have taken for simplicity that there are equal numbers of sectors with positive and negative $m_H^2$, but this assumption does not affect our analysis. This $N$naturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder. The one exception to this is that ``our" sector must consist of the Standard Model.

@@

The ``exotic sectors'' with $i<0$ provide a radical departure from our own. $m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$\draftnote{~\cite{}}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances. The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet. This leads to very light fermions: 
